Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-21 paper/paper.tex
Addressing some of Ewa's comments from 5.4

We assume that we have runtime estimates for each task in the workflow based on
either a performance model of the application, or historical data that can be
mined. In particular, in this study we use workflows from the synthetic workflow
generator~\cite{Bharathi08}.

@@

This paper focuses on scheduling and provisioning for workflow ensembles. A
workflow ensemble consists of several related workflows that a user wishes to
run. Each workflow in an ensemble is given a priority that indicates how
important the workflow is to the user.

The goal of this workflow ensemble scheduling and cloud provisioning problem is
to complete as many high-priority workflows as possible given a fixed budget and
deadline.

@@

These observations are further confirmed when examining the effective computing
cost, as shown in Fig.~\ref{fig:cost}. It can be seen that lower resource
utilization and lower parallel efficiency for short deadlines lead to
substantial increases in the effective computing cost. This increase can be 
significant. For example, a SIPHT ensemble with short deadlines and a budget
of \$1,000 has an effective computing cost $\sim$8--20\% higher than the 
normal cost, depending on the algorithm used. That means that out of the 
\$1,000 budget, \$80--\$200 is spent on idle resources.

>>>>

We assume that we have runtime estimates for each task in the workflow based on
either a performance model of the application, or historical data that can be
mined. In this study we use synthetic workflows that were generated using 
historical data from real applications~\cite{Bharathi08}. These applications 
come from a wide variety of domains including: bioinformatics (Epigenomics, 
SIPHT), astronomy (Montage), earthquake science (CyberShake), and physics 
(LIGO).

@@

This paper focuses on scheduling and provisioning for workflow ensembles. A
workflow ensemble consists of several related workflows that a user wishes to
run. Each workflow in an ensemble is given a priority that indicates how
important the workflow is to the user. These priorities are absolute in the 
sense that completing a high priority workflow is more valuable than 
completing all lower priority workflows combined.

The goal of this workflow ensemble scheduling and cloud provisioning problem is
to complete as many high-priority workflows as possible given a fixed budget and
deadline. Only workflows for which all tasks are finished by the deadline are 
considered to be complete---partial results are not usable in this model.

@@

These observations are further confirmed when examining the effective computing
cost, as shown in Fig.~\ref{fig:cost}. It can be seen that lower resource
utilization and lower parallel efficiency for short deadlines lead to
substantial increases in the effective computing cost. This increase can be 
significant. For example, a SIPHT ensemble with short deadlines and a budget
of \$1,000 has an effective computing cost $\sim$8--20\% higher than the 
minimum effective cost of \$1/hour, depending on the algorithm used. That means that out of the 
\$1,000 budget, \$80--\$200 is spent on idle resources.
